Impact of the High Population Events on Urban Mobility: Who is Affected the Most?

### 2019-12-10 manuscript.Rmd
Conclusions

>>>>

The insignificant difference in travel times during these major shocks can be explained by two main reasons: the unchanging state of demographics in a short time span and the efficiency of transportation system in Washington D.C. Since we only look at travel times in a two-week span, it is likely that the demographic census data stays unchanged and thus not having any effect on the city mobility during those times. Additionally, Washington D.C. is known to have one of the safest, cleanest, and most efficient transportation systems nationwide so the increase in population from the large scale public events is also unlikely to act on its urban mobility. Nonetheless, the models give us interesting insights into the role that socioeconomic status and racial background play in geographical mobility, specifically in the case of Washington D.C.

There are a couple of limitations to our model that limit its performance. First, there are infinitely many unobservable characteristics that might affect urban mobility and our data might not perfectly capture those aspects, which leads to variable bias in these results. More importantly, we did not take into accouunt the fact that Washington D.C. is considerably segregated when computing the spatial covariance matrix, so the estimates do not fully represent the correlation between demographics and urban mobility. All in all, the contextual limitations of our chosen model outlined above will bias the estimates and push them further from the truth.
